---
title: "Statistical Inference Project 2"
author: "Frog"
date: "Wednesday, August 06, 2014"
output: html_document
---

### 1. Load the ToothGrowth data and perform some basic exploratory data analyses 

```{r}
library(ggplot2)
data(ToothGrowth)
str(ToothGrowth)
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
qplot(jitter(as.numeric(ToothGrowth$supp)),jitter(as.numeric(ToothGrowth$dose)),
      size=ToothGrowth$len,ylab="dose",xlab="supp")
```

We can see that as the dose increases the length of the teeth increases but comparing the
same dose levels it is difficult to see if the supplement type has an effect. It seems that
the supllement type OJ (factor level 1) produces slightly longer teeth than supplement 
VC (factor level 2)

### 2. Provide a basic summary of the data.

```{r}
summary(ToothGrowth)
```

You ask it, you got it. 

### 3. Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. 

First I would like to test if the dose has an effect so I will split the dataset in just two
parts: dose==0.5 and dose==2 to compare the higher and lower doses and its effect on Teeth length.

```{r}
group1<-ToothGrowth[ToothGrowth$dose==0.5,1]
group2<-ToothGrowth[ToothGrowth$dose==2,1]
```

Now I perform a t test assuming the groups are not paired 

```{r}
t.test(group1,group2,paired=FALSE)
```

We can see that the dose effectively has an effect in tooth growth

Now I do the same for the supplement type

```{r}
group1<-ToothGrowth[ToothGrowth$supp=="VC",1]
group2<-ToothGrowth[ToothGrowth$supp=="OJ",1]
```

I repeat the same test

```{r}
t.test(group1,group2,paired=FALSE)
```

We can also see there is a difference in means so the supplement type also has a role.

### 4. State your conclusions and the assumptions needed for your conclusions. 

I assumed the tests were done in different populations and that the population size is
enough to draw conclusions.

My conclusions is that if you have a tendece to vampirism then you should take supplement OJ.